A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-20 paper.tex
merge

\begin{abstract}
We give a complete classification of twists of supersymmetric Yang-Mills theories in dimensions~$2\leq n \leq 10$.
We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action of the supersymmetry algebra using the language of $L_\infty$ algebras.  For each orbit in the space of square-zero supercharges in the supersymmetry algebra, under the action of the spin group and the group of R-symmetries, we give a description of the corresponding twisted theory.  These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and $BF$ theory. 
\end{abstract}

@@

Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, and where the theory is moreover translation-invariant. Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$. A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action on the fields is extended to an action of the super Lie algebra $\fA$. In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.

@@

These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.  The twisted gauge theories here are all either equivalent to $BF$-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.  Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop, meaning all higher order corrections vanish identically.

@@

  \draw[dotted] (0.5,-7) -- (0.5,7);
  \draw[dotted] (6.4,-7) -- (6.4,7);
  \draw[dotted] (-2,-7) -- (-2,7);
  \draw[dotted] (-3.8,-7) -- (-3.8,7);
  \draw[dotted] (-4.8,-7) -- (-4.8,7);
  \draw[dotted] (-6.3,-7) -- (-6.3,7);
  \draw[dotted] (-7.3,-7) -- (-7.3,7);

@@

\subsection{Conventions}
Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.  For an element $x$ we denote by $|x|\in\ZZ/2\ZZ$ the total degree.

@@

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The \defterm{generalized $BF$ theory} is the classical field theory
\[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg).\]
\label{def:generalizedBF}
\end{definition}

@@

\begin{example}
For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
\end{example}

We will see many $BF$ theories as the output when we twist supersymmetric gauge theories.
In fact, a special case of the definition above also arises when twisting theories of matter.  We will refer to as this as a generalized $\beta\gamma$ system, where the definition will extend that of the usual 2d $\beta \gamma$ system.

@@

\begin{prop}
\label{prop:BFdolbeaultreduction}
Let $X, M, Y'$ be as above.
Fix an $L_\infty$ algebra $\fg$ and consider the generalized $BF$ theory
\[
T^*[-1] {\rm Map}(X \times (Y' \times \CC)_{\rm Dol} \times M_{\rm dR} , B \fg) .
\]
Its dimensional reduction along $p_{\rm Dol}$ is equivalent to the generalized BF theory
\[
T^*[-1] {\rm Map} (X \times Y'_{\rm Dol} \times (M \times \RR)_{\rm dR}, \fg / \fg)
\]
This equivalence is $\SO(V_\RR)$-equivariant.
\end{prop}
\begin{proof}
Note that there is an isomorphism of $L_\infty$ algebras
\[
\Omega^{\bu, \bu} (Y' \times \CC ; \fg) = \Omega^{\bu,\bu}(Y') \otimes \Omega^{0,\bu}(\CC) \otimes \fg[\epsilon]
\]
where $\epsilon$ is a parameter of degree $+1$.
The result then follows from Proposition \ref{prop:BFholomorphicreduction} applied to the $L_\infty$ algebra $\fg[\epsilon]$. 
\end{proof}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^*\right) + \frac{t}{2} \Omega^{-1} B^*\wedge B^*,\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$. Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:8dholomorphictwist})
\[
\xymatrix@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
\Omega^0(\CC^4; \gg)_a \ar[r] \ar@{-->}^{t\id}[ur] & \Omega^{0,1}(\CC^4; \gg)_C \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,2}(\CC^4; \gg)_{B^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,4}(\CC^4; \gg)_{c^*} \ar@{-->}^{t\id}[ur] &
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\end{theorem}

@@

Up to rescaling the antifields, this is the action functional of the required theory, where $A_{0,\bu}, A_{0,\bu}^*$ comprise the fields of holomorphic $BF$ theory with $B_{2,\bu} = A_{0,\bu}^*$, and the remaining fields comprise the fields of the $\beta\gamma$ system with $\beta_{2,1} = \gamma_{0,1}^*$, $\beta_{2,2} = \gamma_0^*$, and $\gamma_{0,2} = \beta_{2,0}^*$.
\end{proof}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4d2holomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varsigma^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varsigma} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\begin{theorem} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized $BF$ theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. Moreover this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

@@

\begin{theorem} \label{2d_minimal_twist_thm}
The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.  
Moreover, this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

@@

%We first perform a change of variables sending $\lambda_0$ to $\lambda_0 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
%We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
%We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
%The resulting action functional is of the form
\[
S_{BF} + \int \dvol t \bigg( -(\chi_{0,1}, A_{0,1}^*) + (a, c^*) + (\Tilde{\psi}_0, \gamma_0^*) + \frac{1}{2} (\beta_{1,0}^*, \gamma_{0,1}^*) \bigg) 
\]
Here $S_{BF}$ is the action functional of holomorphic $BF$ theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic $BF$ theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$. 
This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem}
The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological $BF$ theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem} \label{2d(0,2)}
The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_0^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

The twisted theory is therefore perturbatively equivalent to the theory with BV action 
\begin{align*}
& \int \bigg(\dbar_{A_{0,1}} A_{0} \wedge A_{0,1}^* + (\dbar_{A_{0,1}} \gamma_{0} \wedge \gamma_{0,1}^*) \bigg) + \dvol \bigg( \frac{1}{2}[A_0, A_0]A_0^*+  [\gamma_0, A_0] \gamma_0^*  \bigg).
\end{align*}
This is the action functional of the required theory, where $B_{1,0} = A_{0,1}^*$, $B_{1,1} = A_{0}^* \dvol$ comprise the anti-fields of holomorphic $BF$ theory and $\beta_{1,0} = \gamma_{0,1}^*$,  $\beta_{1,1} = \gamma_0^* \dvol$ comprise the anti-fields of the $\beta\gamma$ system.
\end{proof}

@@

\begin{theorem}\label{2d(0,4)}
The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$. 
\end{theorem}

@@

\begin{theorem}[See also \cite{SWchar}]
The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action. 
\end{theorem}

>>>>

\begin{abstract}
We give a complete classification of twists of supersymmetric Yang-Mills theories in dimensions~$2\leq n \leq 10$.
We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action of the supersymmetry algebra using the language of $L_\infty$ algebras.  For each orbit in the space of square-zero supercharges in the supersymmetry algebra, under the action of the spin group and the group of R-symmetries, we give a description of the corresponding twisted theory.  These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and BF theory. 
\end{abstract}

@@

Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, and where the theory is moreover translation-invariant. Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$, where $\Pi$ indicates that $\Sigma$ is placed in odd $\ZZ/2\ZZ$-degree, with the only nonvanishing Lie bracket given by $\Gamma$. A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action on the fields is extended to an action of the super Lie algebra $\fA$. In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.

@@

These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.  The twisted gauge theories here are all either equivalent to BF-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.  Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop, meaning all higher order corrections vanish identically.

@@

  \draw[dotted] (0.5,-7) -- (0.5,7);
  \draw[dotted] (6.4,-7) -- (6.4,7);
  \draw[dotted] (-2,-7) -- (-2,7);
  \draw[dotted] (-3.8,-7) -- (-3.8,7);
  \draw[dotted] (-4.8,-7) -- (-4.8,7);
  \draw[dotted] (-6.3,-7) -- (-6.3,7);
  \draw[dotted] (-7.2,-7) -- (-7.2,7);

@@

\subsection{Conventions}
Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.  We will write $\Pi E$ to denote $E$ placed in odd $\ZZ/2\ZZ$ degree.  For an element $x$ we denote by $|x|\in\ZZ/2\ZZ$ the total degree.

@@

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The \defterm{generalized BF theory} is the classical field theory
\[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg).\]
\label{def:generalizedBF}
\end{definition}

@@

\begin{example}
For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological BF theory with the BV action
\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
\end{example}

We will see many BF theories as the output when we twist supersymmetric gauge theories.
In fact, a special case of the definition above also arises when twisting theories of matter.  We will refer to as this as a generalized $\beta\gamma$ system, where the definition will extend that of the usual 2d $\beta \gamma$ system.

@@

\begin{prop}
\label{prop:BFdolbeaultreduction}
Let $X, M, Y'$ be as above.
Fix an $L_\infty$ algebra $\fg$ and consider the generalized BF theory
\[
T^*[-1] {\rm Map}(X \times (Y' \times \CC)_{\rm Dol} \times M_{\rm dR} , B \fg) .
\]
Its dimensional reduction along $p_{\rm Dol}$ is equivalent to the generalized BF theory
\[
T^*[-1] {\rm Map} (X \times Y'_{\rm Dol} \times (M \times \RR)_{\rm dR}, \fg / \fg)
\]
This equivalence is $\SO(V_\RR)$-equivariant.
\end{prop}
\begin{proof}
Note that there is an isomorphism of $L_\infty$ algebras
\[
\Omega^{\bu, \bu} (Y' \times \CC ; \fg) = \Omega^{\bu,\bu}(Y') \otimes \Omega^{0,\bu}(\CC) \otimes \fg[\epsilon]
\]
where $\epsilon$ is a parameter of degree $+1$.
The result then follows from Proposition \ref{prop:BFholomorphicreduction} applied to the $L_\infty$ algebra $\fg[\epsilon]$. 
\end{proof}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{\mr{BF}} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^*\right) + \frac{t}{2} \Omega^{-1} B^*\wedge B^*,\]
where $S_{\mr{BF}}$ is the action functional of the holomorphic twist at $t=0$. Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:8dholomorphictwist})
\[
\xymatrix@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
\Omega^0(\CC^4; \gg)_a \ar[r] \ar@{-->}^{t\id}[ur] & \Omega^{0,1}(\CC^4; \gg)_C \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,2}(\CC^4; \gg)_{B^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,4}(\CC^4; \gg)_{c^*} \ar@{-->}^{t\id}[ur] &
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$. 
Moreover, the equivalence is $\U(2)$-equivariant.
\end{theorem}

@@

Up to rescaling the antifields, this is the action functional of the required theory, where $A_{0,\bu}, A_{0,\bu}^*$ comprise the fields of holomorphic BF theory with $B_{2,\bu} = A_{0,\bu}^*$, and the remaining fields comprise the fields of the $\beta\gamma$ system with $\beta_{2,1} = \gamma_{0,1}^*$, $\beta_{2,2} = \gamma_0^*$, and $\gamma_{0,2} = \beta_{2,0}^*$.
\end{proof}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{\mr{BF}} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
where $S_{\mr{BF}}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4d2holomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varsigma^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varsigma} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\begin{theorem} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized BF theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. Moreover this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

@@

\begin{theorem} \label{2d_minimal_twist_thm}
The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.  
Moreover, this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

@@

%We first perform a change of variables sending $\lambda_0$ to $\lambda_0 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
%We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
%We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
%The resulting action functional is of the form
\[
S_{\mr{BF}} + \int \dvol t \bigg( -(\chi_{0,1}, A_{0,1}^*) + (a, c^*) + (\Tilde{\psi}_0, \gamma_0^*) + \frac{1}{2} (\beta_{1,0}^*, \gamma_{0,1}^*) \bigg) 
\]
Here $S_{\mr{BF}}$ is the action functional of holomorphic BF theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.

@@

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$. 
This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem}
The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{theorem} \label{2d(0,2)}
The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
This equivalence is $\U(1)$-equivariant.
\end{theorem}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_0^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

The twisted theory is therefore perturbatively equivalent to the theory with BV action 
\begin{align*}
& \int \bigg(\dbar_{A_{0,1}} A_{0} \wedge A_{0,1}^* + (\dbar_{A_{0,1}} \gamma_{0} \wedge \gamma_{0,1}^*) \bigg) + \dvol \bigg( \frac{1}{2}[A_0, A_0]A_0^*+  [\gamma_0, A_0] \gamma_0^*  \bigg).
\end{align*}
This is the action functional of the required theory, where $B_{1,0} = A_{0,1}^*$, $B_{1,1} = A_{0}^* \dvol$ comprise the anti-fields of holomorphic BF theory and $\beta_{1,0} = \gamma_{0,1}^*$,  $\beta_{1,1} = \gamma_0^* \dvol$ comprise the anti-fields of the $\beta\gamma$ system.
\end{proof}

@@

\begin{theorem}\label{2d(0,4)}
The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$. 
\end{theorem}

@@

\begin{theorem}[See also \cite{SWchar}]
The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action. 
\end{theorem}
